Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-28 paper.tex
Edit Trading Model

Brokers certify session keys as well. However, it is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss. Therefore, Blind signature is used to prevent the situation. When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contact after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key to the broker. The broker signs the message and returns the signature to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key. Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{key_certification}
	\caption{Session key certification with blind signature}
	\label{fig:key_certification}
\end{figure}

@@

\subsection{Trading}
Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the subscriber list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers. The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each subscriber. After that, the data provider can also get public keys of each subscriber from the Registration Contact with their accounts. For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext to the Product Contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature. Consumers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session¸

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{key_exchange}
	\caption{Session key exchange between the data provider and consumer}
	\label{fig:key_exchange}
\end{figure}

\subsection{Refunding}
It is probable that the sensor is malfunctioning after the consumers pay the subscription fee. To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel. If the expected data is not available, consumers can ask for refunds. We assume that less than half of consumers in the Product Contract are irrational and malicious. Each subscriber can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th data samples, the subscription fee is proportionally transfered to the data provider, broker and every subscriber. The subscription fee can be prorated as below:

@@

Where $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ is the brokerage fee(\%), $F_{t}$ is the transaction fee of the smart contract(\%), $N$ is the number of subscribers in this contract.

>>>>

Brokers certify session keys as well. However, it is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss. Therefore, Blind signature is used to prevent the situation. Figure \ref{fig:key_certification} shows the certification process. When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contact after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key to the broker. The broker signs the message and returns the signature to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key. Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{key_certification}
	\caption{Session key certification process with blind signature.}
	\label{fig:key_certification}
\end{figure}

@@

\subsection{Trading}
Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumer list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}. The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each consumer. After that, the data provider can also get public keys of each consumer from the Registration Contact with their accounts. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext to the Product Contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature. Consumers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session¸

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{key_exchange}
	\caption{Session key exchange process between the data provider and consumer.}
	\label{fig:key_exchange}
\end{figure}

\subsection{Refunding}
It is probable that the sensor is malfunctioning after the consumers pay the subscription fee. To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel. If the expected data is not available, consumers can ask for refunds. We assume that less than half of consumers in the Product Contract are irrational and malicious. Each consumer can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer. The subscription fee can be prorated as below:

@@

where $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ is the brokerage fee(\%), $F_{t}$ is the transaction fee of the smart contract(\%), $N$ is the number of consumers in this contract.

To refund or withdraw subscription fee from the smart contract, data provider, broker, and consumer send a transaction to execute the smart contract and are responsible for transaction fee. We assume that only a half of the expected records are uploaded to the MAM channel. For the data provider and broker, they can withdraw a half of total subscription fee from the smart contract and $F_{b}$ \% belongs to the broker while the remaining belongs to the data provider. For consumers, they can get a half refund which should be deducted the transaction fee.
